---
title: "Solution I"
author: "Ulf Schepsmeier"
date: "12 Mai 2016"
output: html_document
---

Load the package if not yet loaded.
```{r}
library(VineCopula)
```

Load the data set from the package and select the columns of interest.
```{r}
# Load data
data(daxreturns)

# select columns
colnames(daxreturns)
select <- c(1,4,6,11)
dat <- daxreturns[,select]
dat <- as.copuladata(dat)
```

You can see most of the data properties in one plot!
The `pairs()` command plot contour plots (shape, tail dependence), 
histogramms (are the data uniform distributed),
and estimates Kendall's tau.
```{r}
pairs(dat)
```


If you want to do it in separate functions...
```{r}
# Kendall's tau
cor(dat, method = "kendall")

# contour plots
BiCopMetaContour(u1=dat[,1], u2=dat[,2])
BiCopMetaContour(u1=dat[,1], u2=dat[,3])
BiCopMetaContour(u1=dat[,1], u2=dat[,4])

BiCopMetaContour(u1=dat[,2], u2=dat[,3])
BiCopMetaContour(u1=dat[,2], u2=dat[,4])
BiCopMetaContour(u1=dat[,3], u2=dat[,4])
```

A nicer empirical contour plot can be achieved by using better kernal density estimators.
There is one in the package `kdecopula`.
```{r, eval=FALSE}
# nicer with kdecopula
library(kdecopula)
fit <- kdecop(dat[,1:2])
contour(fit)
```

Another graphical function is the `BiCopLambda()` function. Each copula has its characteristic shape.
```{r}
cop <- BiCop(family=3, par=BiCopTau2Par(family=3,
                                        tau = cor(dat[,1:2], method="kendall")[1,2]))
op <- par(mfrow = c(1, 3))
BiCopLambda(u1=dat[,1], u2=dat[,2])  # empirical lambda-function
BiCopLambda(cop)	# theoretical lambda-function
BiCopLambda(u1=dat[, 1], u2=dat[, 2], cop)	# both
par(op)
```

**suggestions for the pairs:**

ALV-BMW: Clayton or survival Gumbel  

ALV-DBK: Student's t-copula  

ALV-MUV2: Student's t-copula  

BMW-DBK: t or a BB-copula (there may be asymmetric tails)  

BMW-MUV2: t or a BB-copula (there may be asymmetric tails) 

DBK-MUV2: t  


If we use the Akaike Information Criterion as comparison measure we get
```{r, cache=TRUE}
BiCopSelect(u1=dat[,1], u2=dat[,2])
BiCopSelect(u1=dat[,1], u2=dat[,3])
BiCopSelect(u1=dat[,1], u2=dat[,4])
BiCopSelect(u1=dat[,2], u2=dat[,3])
BiCopSelect(u1=dat[,2], u2=dat[,4])
BiCopSelect(u1=dat[,3], u2=dat[,4])
```

With BIC we get a similar picture ...
```{r}
BiCopSelect(u1=dat[,1], u2=dat[,2], selectioncrit="BIC")
```
We can also do some goodness-of-fit tests.
```{r}
BiCopGofTest(u1=dat[,1], u2=dat[,2], family = 3, B=0)
```

The p-value is smaller than 0.05. Thus the copula does not fit the data good enough.

The rotated Gumbel copula is better...
```{r}
BiCopGofTest(u1=dat[,1], u2=dat[,2], family = 14)
```

Beside the White GOF test we can use the gof test based on Kendall's transformation function.
```{r, cache=TRUE}
BiCopGofTest(u1=dat[,1], u2=dat[,2], family = 3, method = "kendall") # p-value = 0
BiCopGofTest(u1=dat[,1], u2=dat[,2], family = 14, method = "kendall") # p-value > 0.05
```

Another goodness-of-fit is one based on scores 
```{r, eval=FALSE}
BiCopVuongClarke(u1=dat[,1], u2=dat[,2], familyset = c(1:10, 13,14,16:20,104,204,114,214))
```

