---
title: "Solution III"
author: "Ulf Schepsmeier"
date: "16 Mai 2016"
output: html_document
---

Load the package if not yet loaded.
```{r}
library(VineCopula)
```

Get some data from the package. I selected here the first 6 stock returns.
```{r data}
data("daxreturns")
dat <- daxreturns[,1:6]
```

### Model selection

Fit an R-vine with only Gaussian copulas
```{r Gauss, cache=TRUE}
RVMgauss <- RVineStructureSelect(data = dat, familyset=1, type="RVine")

summary(RVMgauss)
```

Fit an R-vine with arbitrary copula families
```{r RVine, cache=TRUE}
RVM <- RVineStructureSelect(data=dat)
summary(RVM)
```

We can do it also in parallel.
```{r parallel, eval=FALSE}
RVM2 <- RVineStructureSelect(data=dat, cores=4)
```

And finally a C-vine:
```{r Cvine, cache=TRUE}
RVMcvine <- RVineStructureSelect(data=dat, type="CVine")

summary(RVMcvine)
```

### Model comparison based on log-likelihood, AIC and BIC

Summary of the log-lik, AIC, BIC. Make it nice in a table.
```{r}
tab <- data.frame(names=c("Gauss", "R-Vine", "C-Vine"),
                  loglik=c(RVMgauss$logLik, RVM$logLik, RVMcvine$logLik),
                  AIC=c(RVMgauss$AIC, RVM$AIC, RVMcvine$AIC),
                  BIC=c(RVMgauss$BIC, RVM$BIC, RVMcvine$BIC))
tab
```


### Model comparison based on Vuong Test

```{r}
RVineVuongTest(data=dat, RVM1=RVMgauss, RVM2=RVM)
```
Test statistic is negativ => second model is better  
p-value smaller than 0.05 => significant

```{r}
RVineVuongTest(data=dat, RVM1=RVMgauss, RVM2=RVMcvine)
# C-vine > Gauss

RVineVuongTest(data=dat, RVM1=RVM, RVM2=RVMcvine)
# R-vine > C-vine
```

### Model improvment via MLE

```{r MLE, eval=FALSE}
RVMmle <- RVineMLE(data=dat, RVM=RVM)
RVM$loglik
RVMmle$loglik
# Yes a little bit
```

### Truncation

```{r truncation, cache=TRUE}
RVMtrunc <- RVineStructureSelect(data=dat, trunclevel = 2)
RVMtrunc$AIC
RVM$AIC
# Gap of 100 AIC points

RVMtrunc2 <- RVineStructureSelect(data=dat, trunclevel = 3)
RVMtrunc2$AIC
RVM$AIC
# Gap of 30 AIC points => OK
```

